Timeliness of security updates for Android

### 2014-08-13 security_scoring.tex
Add full version graphs for best and worst models to show that they are reasonably classed as such

\daTabSecScoresmodel
Even within manufacturers different models can have very different update behaviours and hence security.
Table~\ref{tab:sec_model} shows the results for the \daNumSigModels\ device models which have a significant presence by the same metric with \daSecScoreBestmodel\ (\daSecScoreBestmodelScore\ / 10) doing best and \daSecScoreWorstmodel\ (\daSecScoreWorstmodelScore\ / 10) doing worst.

>>>>

\daTabSecScoresmodel
Even within manufacturers different models can have very different update behaviours and hence security.
Table~\ref{tab:sec_model} shows the results for the \daNumSigModels\ device models which have a significant presence by the same metric with \daSecScoreBestmodel\ (\daSecScoreBestmodelScore\ / 10) doing best and \daSecScoreWorstmodel\ (\daSecScoreWorstmodelScore\ / 10) doing worst.
We can then test whether this seems fair by comparing the version data for the best and worst models.
Figure~\ref{fig:worst_model_full} shows the full version distribution for \daSecScoreWorstmodel\ and Figure~\ref{fig:best_model_full} shows the same for \daSecScoreBestmodel\ there is a marked difference in the distribution of updates between the two with only \daSecScoreWorstmodelNumFullVersions\ full versions for \daSecScoreWorstmodel\ and \daSecScoreBestmodelNumFullVersions\ for \daSecScoreBestmodel.

\begin{figure}
 \centering
 \begin{subfigure}[b]{\columnwidth}
 \includegraphics[width=\columnwidth]{figures/full_version_\daSecScoreWorstmodel.pdf}
 \caption{\daSecScoreWorstmodel}
 \label{fig:worst_model_full}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
 \includegraphics[width=\columnwidth]{figures/full_version_\daSecScoreBestmodel.pdf}
 \caption{\daSecScoreBestmodel}
 \label{fig:best_model_full}
\end{subfigure}
\caption{Full version distributions for the best and worst model}
\end{figure}
